Alien species

### 2023-09-28 alien_species.Rmd
Specify that indicators are unique also to each ecosystem #83

The nature type mapping is not random and cannot be said to be area
representative. The ANO data set however, is area representative. The
data is from 2018 to present. The data from one field season usually
becomes available early the following year.

>>>>

The nature type mapping is not random and cannot be said to be area
representative. 
This will not improve over time either.

The ANO data set however, is area representative. The
data is from 2018 to present. The data from one field season usually
becomes available early the following year.

Regarding update frequency, the Nature type data set is not replicated, nor will it be in the future. We must therefore trust that the selection criteria for which areas to survey will not change drastically and systematically over time. For example, we are now surveying a lot in pressure areas, meaning lowland areas close to human population centers. If we in the future allocate more time to surveying wilderness areas, then the indicator becomes biased. On the other hand, ANO is replicated every 5 years.
